Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2022-05-31 manuscript.Rmd
Revert "try to load encoding"
This reverts commit 054312fd65f3212acfa70dc598322ce81056cc79.

options(
  tikzDefaultEngine = "xetex",
  tikzXelatexPackages = c(
    getOption("tikzXelatexPackages"),
    "\\usepackage{amsfonts}",
    "\\usepackage[utf8]{inputenc}",
    "\\usepackage{libertine}"
  )
)
```

>>>>

options(
  tikzDefaultEngine = "xetex",
  tikzXelatexPackages = c(getOption("tikzXelatexPackages"), "\\usepackage{amsfonts}", "\\usepackage{libertine}")
)
```
